Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: change the experimental setup label
chore: more on the simulated env

In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
\begin{algorithm}
  \caption{Neighboring-Based Deep Q-Learning}
  \label{alg:neighbor_dqn}
  \ForEach{agent $i \in N$}{
      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
      Initialize replay buffer $\mathcal{D}^i$
  }
  \For{episode = 1 to M}{
      \ForEach{agent $i \in N$}{
          Initialize initial observation $o_0^i$
      }
      \For{t = 0 to T}{
          \ForEach{agent $i \in N$}{
              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{D}^i$\\
              Sample a mini-batch from $\mathcal{D}^i$\\
              Calculate target values using chosen neighboring strategy (see below)\\
              Update $\theta^i$ by minimizing the TD error\\
              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
              \textbf{
              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
          }
      }
  }
\end{algorithm}
\section{Experimental Setup}\label{sec:experiments}

@@

\subsection{Environment} 
First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
  called \emph{collect the items}. % -- see \Cref{fig:env}.
%
This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
 are randomly placed.
%
The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
%
In particular, each agent has an observation space defined by three main parameters, namely: 
\begin{enumerate*}[label=(\roman*)]
  \item number of closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
Regarding the action space, each agent has $8$ possible moves, namely the possible direction on a grid 
  (up, down and diagonal).

\subsection{Reward}
One of the most important aspects in MARL is how the reward signal that the agents use to 
  learn is defined.
%
In particular, we have defined a reward function composed of many subcomponents.

>>>>

In \Cref{alg:neighbor_dqn} we provide a detailed description of the integration of the neighboring-based strategies with deep Q-learning.
\begin{algorithm}
  \caption{Neighboring-Based Deep Q-Learning}
  \label{alg:neighbor_dqn}
  \ForEach{agent $i \in N$}{
      Initialize Q-network $Q^i(o^i, a^i; \theta^i)$ and target network $Q^{i-}(o^i, a^i; \theta^{i-})$\\
      Initialize replay buffer $\mathcal{D}^i$
  }
  \For{episode = 1 to M}{
      \ForEach{agent $i \in N$}{
          Initialize initial observation $o_0^i$
      }
      \For{t = 0 to T}{
          \ForEach{agent $i \in N$}{
              Select action $a_t^i$ based on $\epsilon$-greedy policy using $Q^i(o_t^i, a^i; \theta^i)$\\
              Execute action $a_t^i$ and observe reward $r_{t+1}^i$ and next observation $o_{t+1}^i$\\
              Store $(o_t^i, a_t^i, r_{t+1}^i, o_{t+1}^i)$ in $\mathcal{D}^i$\\
              Sample a mini-batch from $\mathcal{D}^i$\\
              Calculate target values using chosen neighboring strategy (see below)\\
              Update $\theta^i$ by minimizing the TD error\\
              Every C steps, update target network $\theta^{i-} \leftarrow \theta^i$\\
              \textbf{
              Every S steps, perform neighbor interaction (e.g., averaging, consensus, experience sharing)}
          }
      }
  }
\end{algorithm}
\section{Experimental setup}\label{sec:experiments}

@@

\subsection{Simulated environment}
The proposed multi-agent environment, which we design to evaluate the efficacy of the neighboring-based strategies,
 consists of a two-dimensional Euclidean space 
 populated by a variable number of \emph{targets} and \emph{agents}, 
 whose initial positions are randomly distributed across the space.
%
The agents' objective  is to collaboratively collect all the targets in the environment, minimizing the total retrivial time.
%
The observation space of each agent consist of a tuple of three elements: %% TODO CHECK AGAIN
\begin{enumerate*}[label=(\roman*)]
  \item number of the closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of the closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
The action space for each agent is discrete, 
consisting of eight possible movements corresponding 
to the cardinal and diagonal directions on a grid

This setup was chosen as it presents a challenging coordination problem that requires agents to learn both individual target-seeking behaviors and collaborative strategies for reducing the overall retrivial time, 
offering a suitable testbed for evaluating the effectiveness of the proposed neighbor-based decentralized training approaches.
\subsection{Reward}
One of the most important aspects in MARL is how the reward signal that the agents use to 
  learn is defined.
%
In particular, we have defined a reward function composed of many subcomponents.
